Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-18 CAV2018/paper.tex
change citation from arxiv to CAV'17 paper

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective
goes beyond classical stability.  Recent
work~\cite{abate2017automated} described a method for synthesizing
safe digital stabilizing controllers for fully observable LTI plants.
This work differs from the vast majority of existing approaches in
that it explores the continuous space of the system to synthesize
correct-by-construction minimal digital controllers.  In contrast to
LTL models, which require thousands of states and elaborate algorithms
to implement~\cite{reissig2017feedback}, these PID-like controllers
are represented by a few parameters and only require few lines of
code, thus reducing the implementation cost and execution time while
remaining resilient to the effects of digitalization.
However,~\cite{abate2017automated}~is restricted to fully observed
systems (i.e., where all the states are known) modeled in discrete
time, and furthermore explores only a subset of the properties that
engineers are interested in.  By contrast, in most real
implementations, the internal state of a plant cannot be directly
measured but has to be inferred from its effect on the output. A
system that converges to the internal state of the plant from
measurements of its input and output is called an \emph{observer}, and
it is a well known paradigm in the control
literature~\cite{astrom1997computer}.

In this paper we build on the ideas presented in~\cite{abate2017automated}
and develop a new technique that addresses most of these limitations. 
By~combining state-of-the-art synthesis and verification engines we
automatically generate digital \emph{observer controllers} for a given
continuous plant model that are correct by construction.
%
%% This approach delivers a high
%% degree of automation, promises to reduce the cost and time of development of
%% digital control dramatically, and requires considerably less expertise than
%% a-posteriori verification.
%
Specifically, we synthesize stable, software-implemented embedded
controllers along with a model of a physical plant (observer).  Due to the
complexity of such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers meeting a
number of properties that define their desired behavior.

>>>>

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective
goes beyond classical stability.  Recent
work~\cite{DBLP:conf/cav/AbateBCCDKKP17} described a method for synthesizing
safe digital stabilizing controllers for fully observable LTI plants.
This work differs from the vast majority of existing approaches in
that it explores the continuous space of the system to synthesize
correct-by-construction minimal digital controllers.  In contrast to
LTL models, which require thousands of states and elaborate algorithms
to implement~\cite{reissig2017feedback}, these PID-like controllers
are represented by a few parameters and only require few lines of
code, thus reducing the implementation cost and execution time while
remaining resilient to the effects of digitalization.
However,~\cite{DBLP:conf/cav/AbateBCCDKKP17}~is restricted to fully observed
systems (i.e., where all the states are known) modeled in discrete
time, and furthermore explores only a subset of the properties that
engineers are interested in.  By contrast, in most real
implementations, the internal state of a plant cannot be directly
measured but has to be inferred from its effect on the output. A
system that converges to the internal state of the plant from
measurements of its input and output is called an \emph{observer}, and
it is a well known paradigm in the control
literature~\cite{astrom1997computer}.

In this paper we build on the ideas presented in~\cite{DBLP:conf/cav/AbateBCCDKKP17}
and develop a new technique that addresses most of these limitations. 
By~combining state-of-the-art synthesis and verification engines we
automatically generate digital \emph{observer controllers} for a given
continuous plant model that are correct by construction.
%
%% This approach delivers a high
%% degree of automation, promises to reduce the cost and time of development of
%% digital control dramatically, and requires considerably less expertise than
%% a-posteriori verification.
%
Specifically, we synthesize stable, software-implemented embedded
controllers along with a model of a physical plant (observer).  Due to the
complexity of such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers meeting a
number of properties that define their desired behavior.
